Anonymous provision of services via blockchain

### 2022-12-02 paper/access.tex
update paper

@@

Below we describe each step and rationale of the outcome position.

>>>>

\section{Experiments}\label{sec:experiments}

\subsection*{Setup}

We have developed a prototype of our protocol using the following technologies:

\begin{itemize}
  \item{Anonymous payments} — we use the Monero blockchain \cite{monero-blockchain}.
  \item{Storage netowork} — we use the Powergate, which is a wrapper around Filecoin and IPFS \cite{ipfs}.
  \item{Message board} — we use the Ethereum blockchain \cite{ethereum-blockchain}; concretely, Truffle Ganache and Solidity language.
  \item{Customer and SP} — we create client-side web application (webapp) using React for UI, web3.js for interaction with Ethereum, and crypto-js for encryption. We use MetaMask browser extension for signing and submiting transactions to Ethereum's node. We use `monerod` and `monero-wallet-cli' command-line tools for interacting with Monero blockchain.
\end{itemize}

The prototype is available at \url{https://anonser.stan.bar}. The source code is available at \url{https://github.com/stanbar/anonymous-provision-of-services-via-blockchain}.

We developed and tested our prototype in the following environment:

\begin{itemize}
  \item{OS} — Arch Linux 5.11.8
  \item{Docker} — 20.10.5
  \item{CPU} — Intel(R) Core(TM) i7-4790 (8) 4.00~GHz
  \item{RAM} — 16 GB DDR3
  \item{Storage} — Samsung PM85 256~GB SSD

  \item{monerod and monero-wallet-cli} — v0.18.1.2-release
  \item{Powergate} — v0.1.6 // get the version from `docker ps`
  \item{Ganache} — v7.5.0
  \item{Solidity} — v0.8.17
  \item{ReactJS} — v18.0.25
  \item{web3.js} — v1.8.1
  \item{crypto-js} — v4.1.1
\end{itemize}

For simplicity, all components run on one, mentioned above, physical machine; and all processes are managed by Docker.

Moreover, Powergate (storage network) is configured to use local Filecoin and IPFS networks.
For Ethereum blockchain we use Truffle Ganache, which is a local Ethereum blockchain for development and testing purposes. 
Monero is configured to use the public stage network.

\subsection*{Experiments}

\paragraph{Preparation}

Both customer and SP create a Monero wallets using `monero-wallet-cli' command-line tool.

Service provider deploys the smart contract using the `truffle migrate --network development` command, which deploys the smart contract to the local Ethereum blockchain. The webapp is configured to use the latest deployed smart contract address.

Customer get some testing funds using \url{https://community.rino.io/faucet/stagenet/} faucet service.

Next, the customer enable per-transaction proof generation by setting `set store-tx-info 1` for his wallet.  The proof generation is required to verify the payment in case of dispute.

At this point both the customer and the SP are ready to start the protocol.

\paragraph{Experiment}

Service Provider (SP) and Customer (C) are two different users of our prototype, but for simplicity they use the same machine and the same web application.

Now we describe the experiments we performed to test our protocol.

1. The protocol starts with the Customer opening the webapp and creating new provision. 
The app generates random ECDSA (secp256k1) client's keypair and random 32 bytes provisionID, then display QR code that encodes both the provisionID and the client's public key. 
The private key must be stored and provided later for the decryption of the results.

2. The Customer prints the QR code and put it on a package.

3. The Customer delivers his package to the SP either: in person, via trusted party, or delivery agency.

4. The SP opens the app, scans the QR code decoding the provisionID and the client's public key.

5. Since (in this experiment) the provision has not been paid in cash, the SP submits a Proof of Delivery transaction to the Ethereum blockchain, indicating that fact setting the `paid` flag to `false`, and `paymentAddress` field with dedicated Monero address using `monero-wallet-cli integrated-address`.
 If the provision is paid with cash, the SP proceed to the step 8. Otherwise, the SP waits until the Customer pays for the provision.

6. The Customer (using the webapp) check the transaction status on the Ethereum blockchain invoking `getProvision(clientPubKey, provisionID)`.

7. The Customer (using the `monero-wallet-cli transfer`) sends the payment to the designated in the smart contract `paymentAddress` and stores the .

8. The SP starts providing the service and outputs the file `result.pdf`.

9. The SP uploads the file `result.pdf` on the Filecoin and IPFS networks using Powergate. In result, SP gets the content identifier (`cid`), and `dealID`.

10. The SP submits a Proof of Provision transaction to the Ethereum blockchain by invoking `proofOfProvision(clientPubKey, provisionID, cid, dealID)`.

11. Meantime, the Customer subscribes to the Ethereum and waits until the SP publishes the Proof Of Provision.
 Once the Proof Of Provision is published the Customer downloads the result using either: IPFS network via https://dweb.link/<cid> or Lotus network using `lotus retreive <cid> <minerID>'. Then the results are decrypted using previously stored client's private key.

@@

The description of each step and the rationale of the outcome position is given in the appendix in section \ref{sec:proof-of-fairness}.

\section*{Appendix A: Proof of fairness}\label{sec:proof-of-fairness}
Below we describe each step and rationale of the outcome position.
